### 2020-05-27 4_metg.tex
Fix typos.
Clarify CSCS quote.

The choice of 50\% is also a parameter and is not fundamental to
METG. We use 50\% in our studies to avoid pathologies
associated with lower efficiency thresholds (see
Section~\ref{subsec:peak-performance-and-efficiency}), and also
because it aligns with what we observe in practice. For example, in one supercomputer center's application for new projects, users are instructed to ``select the
most parallel efficient job size (ratio of benchmark speed-up
vs. linear speed-up above 50\%)'' \cite{CSCSReport}, which corresponds
to METG(50\%).

@@

METG has a well-defined
relationship with quantities of interest such as
weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the weak and strong scaling of MPI Task Bench running a stencil pattern at a variety of problem sizes. In these
figures, the vertical axis is shown as wall time to emphasize the
relationship to time-to-solution, but it could equivalently be shown
as task granularity (as the number of tasks per execution is
fixed). Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to appear at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed. At the
very bottom, the lines compress together as running time becomes
dominated by overhead. Note that the countour of the bottom of each
graph is identical and conforms to the METG curve (marked by the red,
dashed line).

>>>>

The choice of 50\% is a parameter and not fundamental to METG. We use
50\% in our studies to avoid pathologies associated with lower
thresholds (see Section~\ref{subsec:peak-performance-and-efficiency}),
and also because it aligns with what we observe in practice. {\color{blue} For
example, one supercomputer center instructs users applying for
projects to run a strong scaling study and then ``select the most
parallel efficient job size,'' i.e., the largest number of nodes with
a ``ratio of benchmark speed-up vs. linear speed-up above 50\%''
\cite{CSCSReport}, which corresponds to METG(50\%).}

@@

METG has a well-defined
relationship with quantities of interest such as
weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the weak and strong scaling of MPI Task Bench running a stencil pattern at a variety of problem sizes. In these
figures, the vertical axis is shown as wall time to emphasize the
relationship to time-to-solution, but it could equivalently be shown
as task granularity (as the number of tasks per execution is
fixed). Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to appear at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed. At the
very bottom, the lines compress together as running time becomes
dominated by overhead. Note that the contours of the bottom of each
graph is identical and conforms to the METG curve (marked by the red,
dashed line).
